Variation generation and mean fitness increase: \\ Necessity is the mother of genetic invention

### 2017-11-16 ms.tex
conditional dispersal remark

Another departure from the \emph{linear variation} assumption of the \emph{reduction principle} for mutation rates involves a mechanism by which the mutation rate increases in individuals of low fitness -- a mechanism first observed in stressed bacteria~\citep{Foster2007}, although not in a constant environment.
\citet{Ram2012} demonstrated that even in a constant environment, modifiers that increase the mutation rate of individuals with below-average fitness increase the population mean fitness, rather than decrease it.
Their analysis assumed  infinite population size and fitness  determined by the number of mutant alleles accumulated in the genotype.
In their models, the only departure from the \emph{reduction principle} assumptions was due to the differential effect the modifier has on different genotypes.
A similar result has been demonstrated for fitness-associated recombination~\citep{Hadany2003a} and for condition-dependent sexual reproduction~\citep{Hadany2007a}, and evidence suggests that both mechanisms are common in nature~\citep{Ram2016}.

>>>>

Another departure from the \emph{linear variation} assumption of the \emph{reduction principle} for mutation rates involves a mechanism by which the mutation rate increases in individuals of low fitness -- a mechanism first observed in stressed bacteria~\citep{Foster2007}, although not in a constant environment.
\citet{Ram2012} demonstrated that even in a constant environment, modifiers that increase the mutation rate of individuals with below-average fitness increase the population mean fitness, rather than decrease it.
Their analysis assumed  infinite population size and fitness  determined by the number of mutant alleles accumulated in the genotype.
In their models, the only departure from the \emph{reduction principle} assumptions was due to the differential effect the modifier has on different genotypes.
A similar result has been demonstrated for conditional dispersal~\citep[Th.~39]{Altenberg2012b}, fitness-associated recombination~\citep{Hadany2003a} and for condition-dependent sexual reproduction~\citep{Hadany2007a}, and evidence suggests that both mechanisms are common in nature~\citep{Ram2016}.
